---
title: "Static Report for Mobile Phone Survey Data"
author: "Martin Ng"
date: "24-10-2024"
output: 
  html_document:
    self_contained: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)
library(data.table)
library(DT)
library(ggplot2)
library(broom)
library(dplyr)
```

```{r source}
source("../constants.R")
source("../functions.R")
```

```{r constants}
top = 5
```

```{r functions}

```

```{r read_data}
dat <- fread("../data/mobilephonesurveydata.csv", verbose = F)
```

```{r define_variables}
# dat[, eval(satisfaction.name) := get(satisfaction.name) / value.max.satisfaction]

dat[, Age_Group := cut(Age, 
                       breaks = c(18, 35, 50, 65, Inf), 
                       right = FALSE, 
                       labels = c("18-34", "35-49", "50-64", "65+"))]

unique.age.groups <- dat[, sort(unique(get(age.group.name)))]
unique.genders <- dat[, sort(unique(get(gender.name)))]

dat[, Income_Group := cut(Income, 
                          breaks = c(-Inf, 50000, 75000, 100000, 150000, Inf), 
                          right = FALSE, 
                          labels = c("Under 50k", "50k-75k", "75k-100k", "100k-150k", "150k+"))]

unique.income.groups <- dat[, sort(unique(get(income.group.name)))]
unique.regions <- dat[, sort(unique(get(region.name)))]
unique.personas <- dat[, sort(unique(get(persona.name)))]

unique.products <- dat[, unique(get(product.name))]

respondent.variables <- c(age.group.name, gender.name, income.group.name, region.name, persona.name)
states.of.engagement <- c(awareness.name, consideration.name, consumption.name, satisfaction.name, advocacy.name)
bp.traits <- names(dat)[grep(pattern = bp.pattern, x = names(dat))]

positive_traits <- c("BP_User_Friendly_0_10", "BP_Fast_0_10", "BP_Battery_Life_0_10", "BP_Camera_0_10", "BP_Sleek_0_10", "BP_Stylish_0_10", "BP_Status_Symbol_0_10", "BP_Good_Screen_Size_0_10")
negative_traits <- c("BP_Boring_0_10", "BP_Bulky_0_10", "BP_Fragile_0_10", "BP_Expensive_0_10")

```

# Calculations {.tabset}


### Q1: Respondent Variables {.tabset}
In percentage terms, how were the survey’s respondents divided into categories for the following variables?
```{r q1}

```

#### Age Group
```{r q1_age.group}
age_results <- plot_respondents_distribution(dat, age.group.name)
age_results$plot
#age_results$table
```

#### Gender

```{r q1_gender}
gender_results <- plot_respondents_distribution(dat, gender.name)
gender_results$plot
#gender_results$table
```

#### Income Group

```{r q1_income.group}
income_group_results <- plot_respondents_distribution(dat, income.group.name)
income_group_results$plot
#income_group_results$table
```

#### Region
 
```{r region}
region_results <- plot_respondents_distribution(dat, region.name)
region_results$plot
#region_results$table
```

#### Persona

```{r persona, fig.width=8, fig.height=6}
persona_results <- plot_respondents_distribution(dat, persona.name)
persona_results$plot
#persona_results$table
```


### Q2:  Segmented Outcomes {.tabset}

#### Part A

What are the **top `r top` products** by **Awareness rates** in the **Northeast**?
```{r q2_a, fig.width=8, fig.height=6}
result_a <- plot_top_products(data = dat, metric = "awareness", region = "Northeast", top_n = top)
result_a$plot
#result_a$table
```

#### Part B

What are the **top `r top` products** by **advocacy rates** among **female** respondents who earn **at least $100,000**?
```{r q2_b, fig.width=8, fig.height=6}
result_b <- plot_top_products(data = dat, metric = "advocacy", gender = "Female", income = 100000, top_n = top)
result_b$plot
#result_b$table
```





### Q3:  Overall Brand Perceptions {.tabset}

What are the **top `r top` brands** by the **overall average perception**?
```{r q3}

top_brands <- calculate_brand_perception(num_products = top)

ggplot(top_brands, aes(x = reorder(Product, Overall_Average_Perception), y = Overall_Average_Perception)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  geom_text(aes(label = round(Overall_Average_Perception, 2)), vjust = -0.3, size = 5) +
  labs(title = "Top 5 Brands by overall average perception", 
       x = "Brand", 
       y = "Average Perception") +
  theme_minimal() + 
  theme(panel.grid = element_blank()) + # Remove gridlines
  coord_flip()

```


### Q4: Gaps in Outcomes {.tabset}


#### Part A

Which `r top` products have the **largest gap** between the **rate of consumption** and the **rate of awareness**?
```{r q4_a}
top_engagement_gap <- top_n_engagement_rates(data = dat, state1 = consumption.name, state2 = awareness.name, num_products = top)

# Create a bar plot to visualize the results
ggplot(top_engagement_gap, aes(x = reorder(Product, difference), y = difference)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  geom_text(aes(label = sprintf("%.2f%%", difference)),  # Format the label as a percentage with 2 decimal place
            vjust = -0.5) +  # Adjust the vertical position of the labels
  labs(title = paste("Top", top, "Products by Consumption vs Awareness Gap"),
       x = "Product",
       y = "Difference (%)") +
  theme_minimal() +
  theme(panel.grid = element_blank()) +
  coord_flip()
```

#### Part B

Which `r top` products have the **largest gap** between the **rate of awareness** and the **average satisfaction**? 
```{r q4_b}
top_engagement_gap <- top_n_engagement_rates(data = dat, state1 = awareness.name, state2 = satisfaction.name, num_products = top)

# Create a bar plot to visualize the results in decreasing order
ggplot(top_engagement_gap, aes(x = reorder(Product, difference), y = difference)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  geom_text(aes(label = sprintf("%.2f%%", difference)),  # Format the label as a percentage with 2 decimal place
            vjust = -0.5) +  # Adjust the vertical position of the labels
  labs(title = "Top 5 Products by Awareness vs Satisfaction Gap",
       x = "Product",
       y = "Difference (%)") +
  theme_minimal() +
  theme(panel.grid = element_blank()) +
  coord_flip()
```


### Q5: Aggregated Engagement {.tabset}

#### Part A

How much impact does respondent's **overall trends in awareness** have for that person's **awareness with Buzzdial phones**?
```{r q5_a, fig.width=8, fig.height=6}
# Calculate Aggregated Awareness Excluding Buzzdial
dat_agg <- dat[get(product.name) != "Buzzdial", .(
    aggregated_awareness = mean(get(awareness.name), na.rm = TRUE)
), by = .(id = get(id.name))]

# Merge aggregated awareness back into the dataset for Buzzdial
dat_merged <- merge(
    dat[get(product.name) == "Buzzdial"], 
    dat_agg, by = "id", all.x = TRUE
)
dat_merged[is.na(aggregated_awareness), aggregated_awareness := 0]

# Fit Logistic Regression Model (using fit.model)
awareness_result <- fit.model(
    dt = dat_merged,
    outcome.name = awareness.name,
    input.names = c("aggregated_awareness", age.group.name, gender.name, 
                      income.group.name, region.name, persona.name),
    model.type = "logistic"
)

# Add column to highlight significant terms for ggplot
awareness_result <- awareness_result %>%
    mutate(Significance = ifelse(`Pr(>|z|)` < 0.05 & Variable != "(Intercept)", "Significant", "Not Significant"))

# Create datatable output
model_summary_table <- awareness_result %>%
    select(Variable, Odds.Ratio, OR.Lower.95, OR.Upper.95, `Pr(>|z|)`) %>%
    arrange(`Pr(>|z|)`)

datatable(model_summary_table, rownames = FALSE, options = list(dom = 't', pageLength = -1)) %>%
    formatStyle(
        columns = c("Odds.Ratio", "Pr(>|z|)"), # Columns to highlight
        backgroundColor = styleInterval(
            c(0.05), # Set the threshold for p-value
            c("lightyellow", "white") # Colors for significance
        )
    )

# Create the Odds Ratio Plot with highlighting using ggplot2
ggplot(awareness_result, aes(x = reorder(Variable, Odds.Ratio), y = Odds.Ratio, color = Significance)) +
    geom_point() +
    geom_errorbar(aes(ymin = OR.Lower.95, ymax = OR.Upper.95), width = 0.2) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "red") + # Reference line at Odds Ratio = 1
    coord_flip() +
    labs(title = "Impact of Awareness and Other Factors on Buzzdial Awareness",
         x = "Variables",
         y = "Odds Ratio",
         caption = "Note: Odds Ratio > 1 indicates a positive effect, < 1 indicates a negative effect. Aggregated awareness reflects cross-product engagement.") +
    theme_minimal() +
    scale_color_manual(values = c("Significant" = "red", "Not Significant" = "black"))

```

**Results**: 

Aggregated awareness has a **`r awareness_result[awareness_result$Variable == "aggregated_awareness", "Significance"]`** negative impact on awareness of Buzzdial phones. The odds ratio of **`r awareness_result[awareness_result$Variable == "aggregated_awareness", "Odds.Ratio"]`** means respondents with higher aggregated awareness of other products are less likely to be aware of Buzzdial phones.

**Interpretation**:

Higher awareness of other brands or products crowds out the likelihood of awareness of Buzzdial phones. Buzzdial faces more difficulty gaining brand awareness among individuals who are already highly familiar with competing products in the same market. This suggests that Buzzdial may need to target audiences with lower existing awareness of competitors or increase its marketing efforts to stand out in a crowded market.

Other variables:

* **Age and gender** are significant factors, with younger individuals and women being more likely to be aware of Buzzdial phones.
* **Region** has a very strong effect, especially in the West and Northeast, indicating possible regional marketing success or regional product appeal.

#### Part B

How much impact does respondent's **overall trends in satisfaction** have for that person's **satisfaction with Buzzdial phones**?
```{r q5_b, fig.width=8, fig.height=6}
# Calculate Aggregated Satisfaction Excluding Buzzdial
dat_agg_satisfaction <- dat[get(product.name) != "Buzzdial", .(
  aggregated_satisfaction = mean(get(satisfaction.name), na.rm = TRUE)
), by = .(id = get(id.name))]  # Explicitly name the 'id' column

# Merge this aggregated satisfaction back into the original dataset for Buzzdial
dat_merged2 <- merge(
  dat[get(product.name) == "Buzzdial"],  # Buzzdial data only
  dat_agg_satisfaction,  # Aggregated satisfaction data
  by = "id",  # Join on respondent ID
  all.x = TRUE  # Keep all Buzzdial records, even if no matching aggregated satisfaction is found
)

# If aggregated satisfaction is NA (no other product data), set it to 0
dat_merged2[is.na(aggregated_satisfaction), aggregated_satisfaction := 0]

# Fit the Linear Regression Model
formula_str <- paste(
  satisfaction.name, "~ aggregated_satisfaction +", 
  age.group.name, "+", gender.name, "+", income.group.name, "+", 
  region.name, "+", persona.name
)

# Convert the character string into a formula
formula <- as.formula(formula_str)

# Fit the linear regression model
linear_model <- lm(
  formula = formula,  # Use the dynamically created formula
  data = dat_merged2
)

# Display the model's results (coefficients, 95% Confidence Intervals, and p-values)
linear_model_summary <- broom::tidy(linear_model, conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  rename(Coefficient = estimate, `Lower_CI` = conf.low, `Upper_CI` = conf.high) %>%
  mutate(Coefficient = round(Coefficient, 3),
         p.value = round(p.value, 3)) %>%
  arrange(p.value)

# Save variables with p-value lower than 0.05
significant_terms <- linear_model_summary %>% filter(p.value < 0.05)

# Add a column to indicate significant terms for highlighting
linear_model_summary <- linear_model_summary %>%
  mutate(Significance = ifelse(p.value < 0.05 & term != "(Intercept)", 
                                 "Significant", "Not Significant"))

# Print the linear model summary
lm_summary_table <- linear_model_summary %>%
  rename(Variable = term, `Pr(>|z|)` = p.value) %>%  
  select(-Significance, -Lower_CI, -Upper_CI)

datatable(lm_summary_table, rownames = FALSE, options = list(dom = 't', pageLength = -1)) %>%
  formatStyle(
    columns = c("Variable", "Pr(>|z|)"),  # Columns to highlight
    backgroundColor = styleInterval(
      c(0.05),  # Set the threshold for p-value
      c("lightyellow", "white")  # Colors: red for p-value < 0.05, white for p-value >= 0.05
    )
  ) 

# Create a bar plot for the linear regression coefficients
ggplot(linear_model_summary, aes(x = reorder(term, Coefficient), y = Coefficient, color = Significance)) +
  geom_point() +
  geom_errorbar(aes(ymin = `Lower_CI`, ymax = `Upper_CI`), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +  # Reference line
  coord_flip() +
  labs(title = "Impact of Satisfaction and Other Factors on Buzzdial Satisfaction",
       x = "Variables", 
       y = "Coefficient") +
  theme_minimal()+
  scale_color_manual(values = c("Significant" = "red", "Not Significant" = "black"))

```

**Results**: 

Aggregated Satisfaction itself has a negative coefficient (**`r linear_model_summary[linear_model_summary$term == "aggregated_satisfaction", "Coefficient"]`**), but it is not significant (**p-value = `r linear_model_summary[linear_model_summary$term == "aggregated_satisfaction", "p.value"]`**), indicating that overall trends in satisfaction with other products have no measurable impact on satisfaction with Buzzdial phones.

**Interpretation**:

Other Variables:

* **Personas Have a Strong Influence**: Personas such as "Consistent Compromiser," "Materialistic Meditator," and "Technological Triumphalist" show positive and significant effects on satisfaction with Buzzdial phones, indicating that individuals who align with these personas are more likely to be satisfied with the product.

* **Age Has a Negative Impact** on Satisfaction: Older individuals, particularly those aged 65+ and 35-49, are less likely to be satisfied with Buzzdial phones, as indicated by the significant negative coefficients. This suggests that satisfaction decreases with age.

* Income Group Impact: **Higher income groups** (particularly those earning $100k-150k) show a **negative** but significant association with satisfaction, meaning that wealthier individuals may be less satisfied with Buzzdial phones. However, the effect is relatively modest.

* Regional Differences: Individuals in the **West** show a marginally significant **negative impact** on satisfaction, while other regions do not show significant results. This suggests that satisfaction might vary by region, but the evidence isn't as strong.

